Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-04 manuscript/draft.Rmd
fix route number
make caveat more specific

Forecasting is an emerging imperative in ecology; as such, the field needs to
develop and follow best practices for conducting and evaluating ecological
forecasts [@clark2001]. We have used a number of these practices (Box 1) in a
single study that builds and evaluates forecasts of biodiversity in the form of
species richness. The results of this effort are both promising and humbling.
When comparing forecasts across sites, many different approaches to forecasting
produce reasonable forecasts (Figure 3). If a site is predicted to have a high
number of species in the future, relative to other sites, it generally does.
However, none of the methods evaluated reliably determined how site-level
richness changes over time (Figure 6), which is generally the stated purpose of
these forecasts. As a result, baseline models, which did not attempt to
anticipate changes in richness over time, generally provided the best forecasts
for future biodiversity. While this study was based on a single data set, its
results are consistent with a growing literature on the limits of ecological 
forecasting, as discussed below.

>>>>

Forecasting is an emerging imperative in ecology; as such, the field needs to
develop and follow best practices for conducting and evaluating ecological
forecasts [@clark2001]. We have used a number of these practices (Box 1) in a
single study that builds and evaluates forecasts of biodiversity in the form of
species richness. The results of this effort are both promising and humbling.
When comparing forecasts across sites, many different approaches to forecasting
produce reasonable forecasts (Figure 3). If a site is predicted to have a high
number of species in the future, relative to other sites, it generally does.
However, none of the methods evaluated reliably determined how site-level
richness changes over time (Figure 6), which is generally the stated purpose of
these forecasts. As a result, baseline models, which did not attempt to
anticipate changes in richness over time, generally provided the best forecasts
for future biodiversity. While this study is restricted to breeding birds in
North America, its results are consistent with a growing literature on the
limits of ecological forecasting, as discussed below.
